---
title: "SDL_R_Main"
author: "Delin Sun"
date: "2023-07-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Aims

This R Markdown document aims at completing analyses using the DS package

## Packages
```{r, echo=FALSE}
if (!require("pacman")) {
  install.packages("pacman")
} # make sure that pacman is installed

pacman::p_load(tidyverse,    # data management
               plyr,         # data manegement
               data.table,   # quick read & write files
               GGally,       # ggpairs plots
               ggseg,        # atlas-based brain maps, cortical / subcortical (e.g. aseg)
               ggsegSchaefer # Schaefer's atlas, e.g. schaefer17_400
)
```

### Authors' info
-- Title page (Author list, affiliation list)
-- Acknowledgement page (Author contributions, Acknowledgments, Conflict of interest)
```{r,echo=FALSE}
source("./DS/DS_authors.R")

# create Word docs of authors, affiliations, acknowledgement, author contribution, and conflict of interest
DS_authors(
  fin = "../Data/PGC-PTSD Authors.xlsx",
  fsheet = "Delin - Dynamic rsFC",
  fnames = c('First Name', 'Middle I.', 'Last Name'),
  faffs = c(
    'Primary Institution',
    'Secondary Institution',
    'Additional Institutions 1',
    'Additional Institutions 2',
    'Additional Institutions 3'
  ),
  fcontr = "Author Contribution",
  fackn  = "Funding to Acknowledge",
  fcoi   = "COI:",
  fout_title_page = '../Results/DS/Drafts/DSdoc_Title.docx',
  fout_ackn_page  = '../Results/DS/Drafts/DSdoc_AuthorContribution_Acknowledgment_COI.docx'
)
```

## plot brain maps
```{r,echo=FALSE}
# subcortical plots
ggseg(
          atlas = 'aseg',
          mapping = aes(fill = region),
          color = 'white',
          position = 'dispersed',
          size = 0.5
        ) +
        theme(
          axis.title.x=element_blank(),
          axis.text.x=element_text(size = 18),
          legend.position = "none"
        )

# cortical plots
ggseg(
          atlas = schaefer17_400,
          mapping = aes(fill = region),
          position = 'stacked'
        ) +
        theme(
          axis.title = element_blank(),
          axis.text.x = element_text(size = 18),
          axis.text.y = element_text(size = 18),
          legend.position = "none"
        )
```
### Bold waveforms
```{r,echo=FALSE}
# load SbjInfo.csv
df <-
  file.path('..', 'Data', 'delin_harmonized_w_exclusions.csv') %>% read_csv(na=c('#NULL!', 'NA')) %>%
  distinct(fID, .keep_all = T) # all subjects' info (N=2841)

# load rois' info
df_roi <- read_excel(file.path('..','Data','network lsit.xlsx'), sheet="Sheet2") %>% dplyr::select(Label_Yeo:S) # (Yeo's 17 cortical networks & subcortical regions) including label, name, x/y/z coordinates

## Calculate SD or corr. coef. per subject
fID1 <- df_sbj$fID[[1]]
# load time series data
fin <- file.path('..','Data','ts',fID1) %>% list.files(pattern='.tsv', full.names=TRUE, recursive=TRUE) # file fullname
df <- fin %>% read.table(sep = '\t', header = F) # time series: TRs x ROIs
colnames(df) <- df_roi$ROI_Yeo # assign roi names
df$TRs <- 1:nrow(df)

# Normalization the BOLD signals
a <- df[c("FreeSurfer_Left-Amygdala","17Networks_LH_ContA_Cingm_1")] %>% sapply(function(x) (x-min(x))/(max(x)-min(x)))

# dataframe for plotting
df1 <- data.frame(
  Time=df$TR * 3,
  L_Amyg=a[,1],
  ACC=a[,2]
)

# ggplot2
df2 <- df1 %>% dplyr::select(c("Time","L_Amyg","ACC")) %>% pivot_longer(cols=!Time, names_to="Regions", values_to="BOLD")# 

df2 %>% ggplot(aes(x=Time, y=BOLD, color=Regions)) + geom_line(linewidth=1) + geom_point() + theme_minimal() + labs(x="Time (sec)", y="Normalized Signals") + scale_colour_manual(labels = c('Left Amygdala', 'Anterior Cingulate Cortex'), values = c("red", "blue")) + theme(legend.position = "top",text = element_text(size=20))
```

### Table 1
```{r,echo=FALSE}
source("./DS/DS_table1.R")

# load cleaned data & cleaned data info
df0      <- file.path('..', 'Data', 'Data_cleaned.csv') %>% fread() %>% as.data.frame()

df <- df0
fmodel <- "~ Age  + Sex + curr_ptsd_sev_harmon + child_trauma_sev_harmon + depression_sev_harmon | curr_ptsd_dx"
fnote <-
  "Note: Continuous variables are presented as Mean ± SD, while categorical variables are presented as Count (Proportion in %).\n 
The column named Statistics shows the statistical outputs of betwee-group comparisons. For categorical variables, the Chi-Square Test of Independence is used when all of the cell counts in a crosstable are more than 5; otherwise, the Fisher’s Exact Test is used.\n
For the comparisons of continuous variables between two independent samples, the Two Sample t test (or Welch’s t test) is employed if the variances are equal (or unequal, estimated by an F test) for the two samples.\n
In the case of comparisons of continuous variables between three or more independent samples, the One-Way ANOVA (or Welch's ANOVA) is employed if the variances are equal (or unequal, examined by the Levene's Test) across samples, and if all samples are normally distributed (examined by a Shapiro-Wilk normality test), and Tukey's ‘Honest Significant Difference’ method is employed to correct for post-hoc comparisons for the significant ANOVA output. The Kruskal-Wallis test is used if the assumption of normality is violated in any group, and the Dunn test is employed for post-hoc comparisons for significant Kruskal-Wallis test output.\n
Missing values are not included in statistical analyses. All tests are two-tailed at the 0.05 level of significance.\n"

# Create Table1 Object, convert to flextable, and change font
tbl1 <- df %>% 
  DS_table1(fmodel, fnote) %>% 
  t1flex() 

tbl1 <- tbl1%>%  
  bold(part="header") %>%  
  italic(j = which("Statistics"==(tbl1 %>% .$header %>% .$dataset %>% colnames()))) # make the column of statistics into italic

tbl1

# Save table into a Word document
tbl1 %>% save_as_docx(path="Table1_example.docx")

```


## pair plots of some clinical variables
```{r,echo=FALSE}
# Function to return points and geom_smooth
# allow for the method to be changed
my_fn <- function(data, mapping, method="lm", ...){
      p <- ggplot(data = data, mapping = mapping) + 
        geom_point(size=0.6) + 
        geom_smooth(method=method, ...) +
        xlim(0, 1) +
        ylim(0, 1)
      p
}

df <- df0 %>% select(c('curr_ptsd_sev_harmon', 'child_trauma_sev_harmon', 'depression_sev_harmon')) %>% mutate(PTSD=curr_ptsd_sev_harmon, Child_Trauma = child_trauma_sev_harmon, Depression = depression_sev_harmon) %>% select(c('PTSD','Child_Trauma','Depression'))

# ggpais plots    
df %>% ggpairs(lower = list(continuous = my_fn))


```



### Statistical Modelling Parameters
-- Models fit (linear regression models, linear mixed effects models, etc.) 
-- Outputs: broom tables (statistical outputs & model estimations)
<!-- -- ggplot2 plots -->
<!-- -- Drafts of Methods & Results (as well as parts of Abstract & Discussion) -->
```{r, echo=FALSE}
# load cleaned data & cleaned data info
df0      <- file.path('..', 'Data', 'Data_cleaned.csv') %>% fread() %>% as.data.frame()
# df0_info <- file.path('..', 'Data', 'Data_cleaned_info.csv') %>% fread() %>% as.data.frame()

df0_info <- NULL # for simple applications

# names of columns as dependent variables (Y)
Yname <- df0 %>% select(starts_with("DFC"), starts_with("SFC")) %>% colnames()

# set the levels of factors
df0$curr_ptsd_dx <- df0$curr_ptsd_dx %>% factor(levels=c('Control', 'PTSD'))
df0$Sex          <- df0$Sex          %>% factor(levels=c('Male', 'Female'))
df0$SITE         <- df0$SITE         %>% factor()

# models
mdls <- c(
  'lmer(y ~ curr_ptsd_dx + Age + Sex + (1|SITE))',
  'lmer(y ~ curr_ptsd_sev_harmon + Age + Sex + (1|SITE))',
  'lmer(y ~ curr_ptsd_dx * Age + Sex + (1|SITE))',
  'lmer(y ~ curr_ptsd_dx * Sex + Age + (1|SITE))',
  'lmer(y ~ curr_ptsd_dx * depression_sev_harmon   + Age + Sex + (1|SITE))',
  'lmer(y ~ curr_ptsd_dx * child_trauma_sev_harmon + Age + Sex + (1|SITE))',
  'lmer(y ~ curr_ptsd_dx * curr_ptsd_sev_harmon + Age + Sex + (1|SITE))'
)

# directory for final statistical results & model estimations
fdir <- file.path('..',  'Results', 'DS', 'Stats')
```


### Run all models
```{r,echo=FALSE}
source("./DS/DS_stat.R")

# # models for main & interaction effects
# for (mdl in mdls){
#   DS_stat(df0, df0_info, Yname, mdl, fdir)
#   print(paste('Finished!!!', mdl))
# }

# # Post-hoc models: curr_ptsd_dx * Age
# df0 %>% filter(curr_ptsd_dx=='Control') %>% DS_stat(df0_info, Yname,
#                   'lmer(y ~ Age + Sex + (1|SITE))', fdir,
#                   '_posthoc_Control_only')
# df0 %>% filter(curr_ptsd_dx=='PTSD') %>% DS_stat(df0_info, Yname,
#                   'lmer(y ~ Age + Sex + (1|SITE))', fdir,
#                   '_posthoc_PTSD_only')
# 
# # Post-hoc models: curr_ptsd_dx * Sex
# df0 %>% filter(curr_ptsd_dx=='Control') %>% DS_stat(df0_info, Yname,
#                   'lmer(y ~ Sex + Age + (1|SITE))', fdir,
#                   '_posthoc_Control_only')
# df0 %>% filter(curr_ptsd_dx=='PTSD') %>% DS_stat(df0_info, Yname,
#                   'lmer(y ~ Sex + Age + (1|SITE))', fdir,
#                   '_posthoc_PTSD_only')
# 
# # Post-hoc models: curr_ptsd_dx * depression_sev_harmon
# df0 %>% filter(curr_ptsd_dx=='Control') %>% DS_stat(df0_info, Yname,
#                   'lmer(y ~ depression_sev_harmon + Age + Sex + (1|SITE))', fdir,
#                   '_posthoc_Control_only')
# df0 %>% filter(curr_ptsd_dx=='PTSD') %>% DS_stat(df0_info, Yname,
#                   'lmer(y ~ depression_sev_harmon + Age + Sex + (1|SITE))', fdir,
#                   '_posthoc_PTSD_only')
# 
# # Post-hoc models: curr_ptsd_dx * child_trauma_sev_harmon
# df0 %>% filter(curr_ptsd_dx=='Control') %>% DS_stat(df0_info, Yname,
#                   'lmer(y ~ child_trauma_sev_harmon + Age + Sex + (1|SITE))', fdir,
#                   '_posthoc_Control_only')
# df0 %>% filter(curr_ptsd_dx=='PTSD') %>% DS_stat(df0_info, Yname,
#                   'lmer(y ~ child_trauma_sev_harmon + Age + Sex + (1|SITE))', fdir,
#                   '_posthoc_PTSD_only')

# Post-hoc models: curr_ptsd_dx * 
df0 %>% filter(curr_ptsd_dx=='Control') %>% DS_stat(df0_info, Yname,
                  'lmer(y ~ curr_ptsd_sev_harmon + Age + Sex + (1|SITE))', fdir,
                  '_posthoc_Control_only')
df0 %>% filter(curr_ptsd_dx=='PTSD') %>% DS_stat(df0_info, Yname,
                  'lmer(y ~ curr_ptsd_sev_harmon + Age + Sex + (1|SITE))', fdir,
                  '_posthoc_PTSD_only')
```

## Brain map Plots: (1) main effect of curr_ptsd_dx
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx + Age + Sex + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='curr_ptsd_dxPTSD', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'),
               fdir = file.path('..','Results','DS','Results'))

```
## Brain map Plots: (1.1) main effect of curr_ptsd_sev_harmon
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_sev_harmon + Age + Sex + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='curr_ptsd_sev_harmon', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'),
               fdir = file.path('..','Results','DS','Results'))
```


## Brain map Plots: (2) curr_ptsd_dx by Age interaction
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x Age + Sex + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='curr_ptsd_dxPTSD:Age', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'),
               fdir = file.path('..','Results','DS','Results'))

```

## Brain map Plots: (3) curr_ptsd_dx by Sex interaction
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x Sex + Age + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='curr_ptsd_dxPTSD:SexFemale', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'),
               fdir = file.path('..','Results','DS','Results'))

```

## Brain map Plots: (3.1) curr_ptsd_dx by Sex interaction
## Post hoc: effect of Sex in Control only
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

fname <- file.path('..','Results','DS','Stats', 
                   paste0('Statistics_lmer(y ~ Sex + Age + (1_SITE), data=.)_posthoc_Control_only','.csv'))
fterm <- 'SexFemale'
fdf0_info <- file.path('..', 'Data', 'Data_cleaned_info.csv')
fmask <- file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x Sex + Age + (1_SITE), data=.)','.csv'))
fmask_term <- 'curr_ptsd_dxPTSD:SexFemale'

DS_plots_ggseg(fname, fterm, fdf0_info)#, fmask, fmask_term)

```

## Brain map Plots: (3.2) curr_ptsd_dx by Sex interaction
## Post hoc: effect of Sex in PTSD only
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

fname <- file.path('..','Results','DS','Stats', 
                   paste0('Statistics_lmer(y ~ Sex + Age + (1_SITE), data=.)_posthoc_PTSD_only','.csv'))
fterm <- 'SexFemale'
fdf0_info <- file.path('..', 'Data', 'Data_cleaned_info.csv')
fmask <- file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x Sex + Age + (1_SITE), data=.)','.csv'))
fmask_term <- 'curr_ptsd_dxPTSD:SexFemale'

DS_plots_ggseg(fname, fterm, fdf0_info)#, fmask, fmask_term)

```


## Brain map Plots: (4) curr_ptsd_dx by depression interaction
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x depression_sev_harmon   + Age + Sex + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='curr_ptsd_dxPTSD:depression_sev_harmon', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'),
               fdir = file.path('..','Results','DS','Results'))
```

## Brain map Plots: (4.1) curr_ptsd_dx by depression interaction
## Post hoc: effect of depression in Control only
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

fname <- file.path('..','Results','DS','Stats', 
                   paste0('Statistics_lmer(y ~ depression_sev_harmon + Age + Sex + (1_SITE), data=.)_posthoc_Control_only','.csv'))
fterm <- 'depression_sev_harmon'
fdf0_info <- file.path('..', 'Data', 'Data_cleaned_info.csv')
fmask <- file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x depression_sev_harmon   + Age + Sex + (1_SITE), data=.)','.csv'))
fmask_term <- 'curr_ptsd_dxPTSD:depression_sev_harmon '

DS_plots_ggseg(fname, fterm, fdf0_info)#, fmask, fmask_term)
```

## Brain map Plots: (4.2) curr_ptsd_dx by depression interaction
## Post hoc: effect of depression in PTSD only
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

fname <- file.path('..','Results','DS','Stats', 
                   paste0('Statistics_lmer(y ~ depression_sev_harmon + Age + Sex + (1_SITE), data=.)_posthoc_PTSD_only','.csv'))
fterm <- 'depression_sev_harmon'
fdf0_info <- file.path('..', 'Data', 'Data_cleaned_info.csv')
fmask <- file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x depression_sev_harmon   + Age + Sex + (1_SITE), data=.)','.csv'))
fmask_term <- 'curr_ptsd_dxPTSD:depression_sev_harmon '

DS_plots_ggseg(fname, fterm, fdf0_info)#, fmask, fmask_term)
```

## Brain map Plots: (5) curr_ptsd_dx by childhood trauma interaction
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x child_trauma_sev_harmon + Age + Sex + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='curr_ptsd_dxPTSD:child_trauma_sev_harmon', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'))
```

## Brain map Plots: (6) curr_ptsd_dx by PTSD severity interaction
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x curr_ptsd_sev_harmon + Age + Sex + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='curr_ptsd_dxPTSD:curr_ptsd_sev_harmon', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'),
               fdir = file.path('..','Results','DS','Results'))
```

## Brain map Plots: (6.1) curr_ptsd_dx by PTSD severity interaction
## Post hoc: effect of PTSD severity in Control only
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

fname <- file.path('..','Results','DS','Stats', 
                   paste0('Statistics_lmer(y ~ curr_ptsd_sev_harmon + Age + Sex + (1_SITE), data=.)_posthoc_Control_only','.csv'))
fterm <- 'curr_ptsd_sev_harmon'
fdf0_info <- file.path('..', 'Data', 'Data_cleaned_info.csv')
fmask <- file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x curr_ptsd_sev_harmon + Age + Sex + (1_SITE), data=.)','.csv'))
fmask_term <- 'curr_ptsd_dxPTSD:curr_ptsd_sev_harmon'

DS_plots_ggseg(fname, fterm, fdf0_info)#, fmask, fmask_term)
```


## Brain map Plots: (6.2) curr_ptsd_dx by PTSD severity interaction
## Post hoc: effect of PTSD severity in PTSD only
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

fname <- file.path('..','Results','DS','Stats', 
                   paste0('Statistics_lmer(y ~ curr_ptsd_sev_harmon + Age + Sex + (1_SITE), data=.)_posthoc_PTSD_only','.csv'))
fterm <- 'curr_ptsd_sev_harmon'
fdf0_info <- file.path('..', 'Data', 'Data_cleaned_info.csv')
fmask <- file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx x curr_ptsd_sev_harmon + Age + Sex + (1_SITE), data=.)','.csv'))
fmask_term <- 'curr_ptsd_dxPTSD:curr_ptsd_sev_harmon'

DS_plots_ggseg(fname, fterm, fdf0_info)#, fmask, fmask_term)
```

## Supplementary Brain map Plots: (1) main effect of Age
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx + Age + Sex + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='Age', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'))

```

## Supplementary Brain map Plots: (2) main effect of Sex
```{r, echo=FALSE}
source("./DS/DS_plots_ggseg.R")

file.path('..','Results','DS','Stats', 
                     paste0('Statistics_lmer(y ~ curr_ptsd_dx + Age + Sex + (1_SITE), data=.)','.csv')) %>% 
DS_plots_ggseg(fterm='SexFemale', 
               fdf0_info = file.path('..', 'Data', 'Data_cleaned_info.csv'))

```



```{r,echo=FALSE}
# representative variable(s)
df1 <- df %>% filter(grepl('DFC_30_50_LAmyg', yname) & adj_p<0.05)
if(dim(df1)[[1]] == 0){
  # if no significance
  print('No significant results!!!')
} else {
  # the variable name (column name) of max & min significant results
  Vname_max <- df1 %>% select(statistic) %>% unlist() %>% which.max() %>% df1[., 'yname'] %>% .[[1]]
  print(paste('Max =', Vname_max, ', T =', round(df1[yname==Vname_max, 'statistic'],3), ', adj_p =', round(df1[yname==Vname_max, 'adj_p'],3)))
  Vname_min <- df1 %>% select(statistic) %>% unlist() %>% which.min() %>% df1[., 'yname'] %>% .[[1]]
  print(paste('Min =', Vname_min, ', T =', round(df1[yname==Vname_min, 'statistic'],3), ', adj_p =', round(df1[yname==Vname_min, 'adj_p'],3)))
}

# lmer package
pacman::p_load(lme4, lmerTest, sjPlot, ggpubr)

    
# model fitting
df <- df0
df$y <- df[,Vname_max] # add roi value as y value
mtxt <- 'lmer(y ~ curr_ptsd_dx + Age + Sex + (1|SITE))'
mtxt <- mtxt %>% gsub("[)]$", ", data=df)",.)
MOD  <- eval(parse(text=mtxt)) # model estimation

plt_max <- MOD %>% plot_model(type='pred', terms='curr_ptsd_dx', axis.title=c('',''), axis.lim = c(.3,.6)) + 
  labs(title='Max') +
  theme_minimal() + theme(axis.text=element_text(size=15), axis.title=element_text(size=15,face="bold"))# + scale_color_manual(values=c( "#56B4E9","#E69F00"))
plt_max

df$y <- df[,Vname_min] # add roi value as y value
mtxt <- 'lmer(y ~ curr_ptsd_dx + Age + Sex + (1|SITE))'
mtxt <- mtxt %>% gsub("[)]$", ", data=df)",.)
MOD  <- eval(parse(text=mtxt)) # model estimation
plt_min <- MOD %>% plot_model(type='pred', terms='curr_ptsd_dx', axis.title=c('',''), axis.lim = c(.4,.5)) + 
  labs(title='Min') +
  theme_minimal() + theme(axis.text=element_text(size=15), axis.title=element_text(size=15,face="bold"))# + scale_color_manual(values=c( "#56B4E9","#E69F00"))
plt_min

plt_effect <- ggarrange(plt_min, plt_max,font.label=list(size=20, face="bold"), common.legend=T)

plt_effect




fig <- ggseg(atlas=schaefer17_400, position='stacked', mapping = aes(fill = region))
fig
a <- fig$data
fwrite(schaefer17_400, 'xxx.csv')
a <- schaefer17_400
```


