---
title: "SDL_R_Preprocessing"
output: html_document
date: "2023-09-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aims

The ENIGMA PGC PTSD resting-state functional magnetic resonance imaging (rs-fMRI) have been preprocessed by Courtney Haswell. Here, we need to do some extra preprocessing steps to
--- (1) summarize the head motions (framewise displacement) under different thresholds to test case-control differences.
--- (2) remove linear trends, and regress out the effects of white matter and CSF from time series.
--- (3) make static and dynamic rsFC datasets using the atlas-based timeseries

## Packages
```{r, echo=FALSE}
if (!require("pacman")) {
  install.packages("pacman")
} # make sure that pacman is installed

pacman::p_load(tidyverse,    # data management
               data.table,   # quick read & write files
               foreach,      # parallel processing
               doParallel,   # parallel processing
               GGally,       # ggpairs plots
               pracma       # detrend data
)
```

## Copy from Duke BIAC server the files of timeseries & confounds
```{r,echo=FALSE}
source("./DS/DS_copy.R")

# copy & paste timeseries files
fdir_in  <- "/Volumes/dusom_morey/Data/Lab/new_halfpipe/Outputs/atlas_conn"
fdir_out <- "../Data/BIAC_Server"
fstrings <- "_task-rest_feature-corrMatrix_atlas-schaefer2011Combined_timeseries.tsv"
system.time({
  DS_copy(fdir_in, fdir_out, fstrings)
})


# copy & paste confounds files
fdir_in  <- "/Volumes/dusom_morey/Data/Lab/new_halfpipe/Outputs/confounds"
fdir_out <- "../Data/BIAC_Server"
fstrings <- "-confounds_timeseries.tsv"
system.time({
  DS_copy(fdir_in, fdir_out, fstrings)
})
```


## Data from doc, ts, & confounds
```{r,echo=False}
## Info from SbjInfo_harmon.csv: harmonized clinical/behavioral info provided by Ahmed
df_doc <-
  file.path('..', 'Data', 'delin_harmonized_updated_final.csv') %>% fread(na.strings=c('#NULL!', 'NA')) %>% distinct(fID, .keep_all = T) # all subjects' info (N=2931)

## Info of signals (timeseries, or ts)
# Note: each subject has his/her own folder
# pattern of the filenames of timeseries
fpatt <- "_task-rest_feature-corrMatrix_atlas-schaefer2011Combined_timeseries.tsv"
# fullnames of all files of interest
fn <-  file.path('..','Data','BIAC_Server') %>% 
  list.files(pattern=fpatt, recursive=T, full.names=T) 
# all segments of the filenames
df_ts <- fn %>% 
  strsplit(split = .Platform$file.sep) %>% 
  as.data.frame() %>% t() %>% as.data.frame() %>% 
  mutate(fID=paste0(V11,"_",V12), sig_fullname=fn)
# remove rownames for aesthetic purpose
rownames(df_ts) <- NULL
# just select fID and fullname
df_ts <- df_ts %>% select(c("fID","sig_fullname")) # (N=2413)


## Info of confounds
# Note: all subjects are put together (no individual folder) per SITE
# pattern of the filenames of confounds
fpatt <- "-confounds_timeseries.tsv"
# fullnames of all files of interest
fn <-  file.path('..','Data','BIAC_Server') %>% 
  list.files(pattern=fpatt, recursive=T, full.names=T) 
# all segments of the filenames
df_conf <- fn %>% 
  strsplit(split = .Platform$file.sep) %>% 
  as.data.frame() %>% t() %>% as.data.frame() %>% 
  mutate(fID=paste0(V11,"_", gsub(fpatt,"",V12)), noise_fullname=fn)
# remove rownames for aesthetic purpose
rownames(df_conf) <- NULL
# just select fID and fullname
df_conf <- df_conf %>% select(c("fID","noise_fullname")) # (N=2468)

# Merge df_ts & df_conf
df1 <- df_ts %>% merge(df_conf, by="fID") # (N=2413)

# find the rows in df_doc but not in ts data
a <- setdiff(df_doc$fID, df1$fID) # (N=687)
# find the rows in ts data but not in df_doc
b <- setdiff(df1$fID, df_doc$fID) # (N=169)

# # load Duke_data_supp
# df2 <- file.path('..', 'Data', 'Duke_data_supp.csv') %>% read_csv(na=c('#NULL!', 'NA')) %>% distinct(fID, .keep_all = T)
# 
# # find the data in ts data, not in df_doc, but in Duke_supp
# data.frame(fID=b) %>% merge(df2,by='fID') %>% drop_na() %>% fwrite('Duke_supp.csv')

# Merge df_doc, df_ts, & df_confounds
df0 <- df_doc %>% merge(df1, by="fID") # (N=2244)
```

## Aim 1: Summarize head motions (framewise displacement)
```{r,echo=FALSE}
# function to calculate the frequency of a variable beyond threshold
# Input
# --- x, a vector (or a dataframe column) of numeric values
# --- thr, the threshold value
# Output
# --- the frequency (in %) of variable x above the threshold thr
SDL_freq <- function(x,thr){
  return(sum(x>thr, na.rm=T)*100/length(x))
}

# thresholds for framewise displacement
thrs <- c(0.1, 0.2, 0.3, 0.4, 0.5)
thrs_name <- paste0("thr_",thrs)

# matrix to contain the No. of FD above thresholds
M_DF <- matrix(NA, nrow=dim(df0)[1], ncol=length(thrs))

# Calculate the frequencies of FD above thresholds per subject
for (i in seq(dim(df0)[1])) {
  # confounds (No. time points x No. confounding variables)
  df_con <- df0$noise_fullname[[i]] %>% 
    fread(na.strings = c("n/a")) %>% 
    select(c("csf", "white_matter", "framewise_displacement", "global_signal"))
  
  # 1st FD is NA, change to 0 for lm models
  df_con$framewise_displacement[[1]] <- 0
  
  # calculate the frequencies of FD above thresholds
  freq_FD <- thrs %>%
    sapply(SDL_freq, x = df_con$framewise_displacement)
  
  # fill in the matrix
  M_DF[i, ] <- freq_FD
}

# bind with df0
M_DF <- M_DF %>% as.data.frame()
colnames(M_DF) <- thrs_name
df0 <- df0 %>% cbind(M_DF)

# PTSD-Control differences
source("./DS/DS_table1.R")

df <- df0
fmodel <- "~ thr_0.1 + thr_0.2 + thr_0.3 + thr_0.4 + thr_0.5 | CurrentPTSDDiagnosis"

# Create Table1 Object, convert to flextable, and change font
tbl1 <- df %>% 
  DS_table1(fmodel) %>% 
  t1flex() 

tbl1 <- tbl1%>%  
  bold(part="header") %>%  
  italic(j = which("Statistics"==(tbl1 %>% .$header %>% .$dataset %>% colnames()))) # make the column of statistics into italic

tbl1

# Save table into a Word document
tbl1 %>% save_as_docx(path=file.path("..","Results","Framewise_displacement.docx"))

```

## An example of the correlations between signals and confounds
```{r,echo=FALSE}
i<-1 # ith subject for example

# signals
df_sig <- df0$sig_fullname[[i]] %>% 
  fread()

# confounds
df_con <-
    df0$noise_fullname[[i]] %>% 
    fread(na.strings = c("n/a")) %>% 
    select(c("csf", "white_matter", "framewise_displacement", "global_signal"))

# 1st FD is NA, change to 0 for lm models
df_con$framewise_displacement[[1]] <- 0
  
# combine signals and confounds for regression
df_sig <- df_sig %>% cbind(df_con)

# Function to return points and geom_smooth
# allow for the method to be changed
my_fn <- function(data, mapping, method="lm", ...){
      p <- ggplot(data = data, mapping = mapping) + 
        geom_point(size=0.6) + 
        geom_smooth(method=method, ...)
      p
}

df <- df_sig %>% select(c("V1","csf", "white_matter", "framewise_displacement", "global_signal")) 

# ggpais plots    
df %>% ggpairs(lower = list(continuous = my_fn))

# regression (without global_signal)
V1_corrected_noGlobal <- lm(V1 ~ csf + white_matter + framewise_displacement, data=df_sig) %>% residuals() + mean(df_sig$V1, na.rm=T)
plot(df_sig$V1, V1_corrected_noGlobal)

# regression (with global_signal)
V1_corrected_Global <- lm(V1 ~ csf + white_matter + framewise_displacement + global_signal, data=df_sig) %>% residuals() + mean(df_sig$V1, na.rm=T)
plot(df_sig$V1, V1_corrected_Global)
```


## Aim 2: Regress out confounds (csf, white_matter, framewise_displacement, and maybe global_signal) from timeseries
```{r,echo=FALSE}
source("./DS/DS_denoise.R")
df       <- df0
fdetrend <- "linear"
fcons    <- c("csf","white_matter","framewise_displacement")
fdir_o   <- file.path('..','Processes','ts_corrected_detrend_csf_wm_FD')
DS_denoise(df, fdetrend, fcons, fdir_o)

```


## Aim 3: Static and Dynamic rsFC calculation
```{r,echo=FALSE}
source("./DS/DS_net_FC_para.R")

# # denoised data
# df <- df0 %>% mutate(sig_fullname=file.path('..','Processes','ts_corrected_detrend_csf_wm_FD',paste0(fID,"_signal_denoised.csv")))
# idx <- NULL
# # output to denoised directory
# fdir_o <- file.path('..', 'Processes','FC_corrected_detrend_csf_wm_FD')

## change signal file names for data analyses
# make the output directory
df <- df0
fdir_o <- file.path('..', 'Processes','ts')
dir.create(fdir_o)
# copy signal files to the 
print("Copying files!!! Please be patient...")
for(i in seq(dim(df)[1])){
  file.copy(df$sig_fullname[[i]], 
            file.path(fdir_o, paste0(df$fID[[i]],".tsv"))
            )
}
print("Completed! Copy files. Please double check the files.")

# parameters
df <- df0 %>% mutate(sig_fullname=file.path('..','Processes','ts',paste0(fID,".tsv")))
idx <- NULL
fdir_o <- file.path('..', 'Processes','FC_Matrix')
  
# SFC 
DS_net_FC_para(df, 0, 100, idx, fdir_o) # (win_len=0, win_overlap=100)

# DFC 
DS_net_FC_para(df, 30, 50, idx, fdir_o) # (win_len=30, win_overlap=50)
DS_net_FC_para(df, 30, 25, idx, fdir_o) 
DS_net_FC_para(df, 30, 75, idx, fdir_o) 
DS_net_FC_para(df, 20, 50, idx, fdir_o) 
DS_net_FC_para(df, 40, 50, idx, fdir_o) 

```