---
title: "SDL_R_Clean"
author: "Delin Sun"
date: "2023-07-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aims

This R Markdown document aims at cleaning & organizing the data to meet the requirement of the DS package

## Packages
```{r, echo=FALSE}
if (!require("pacman")) {
  install.packages("pacman")
} # make sure that pacman is installed

pacman::p_load(tidyverse,    # data management
               plyr,         # data manegement
               data.table   # quick read & write files
)
```

## Load raw data files
Including:
--- subjects' demographic & clinical info
--- 4 seed-based dynamic rsFC (tw=30, tp=50) & static rsFC (tw=0, tp=100)
--- cleaned data's info: numeric/categorical, domain, brain atlas

## (1) subjects' demographic & clinical info
```{r, echo=FALSE}
# load SbjInfo_harmon.csv: harmonized clinical/behavioral info provided by Ahmed
df <-
  file.path('..', 'Data', 'delin_harmonized_updated_final.csv') %>% fread(na.strings=c('#NULL!', 'NA')) %>%
  distinct(fID, .keep_all = T) # all subjects' info (N=2931)

# clean & transform variables of interest
# Sex
df$Sex <- df$Sex %>% 
  as.factor() %>% 
  plyr::revalue(c("0"="Male",  "1"="Female")) # according to the defination per SITE

# Current PTSD diagnosis (curr_PTSD_dx)
df$curr_ptsd_dx <- df$CurrentPTSDDiagnosis %>% 
  as.factor() %>% 
  plyr::revalue(c("0"="Control","1"="PTSD"))

# remove subjects without clear curr_PTSD_dx, Age, Sex, or SITE info
# Age & Sex in fact do not have missing values
df <- df %>% 
  filter(!is.na(curr_ptsd_dx) & !is.na(Age) & !is.na(Sex) & !is.na(SITE)) # (N=2931)

# list all subjects' brain data files (one file per subject)
fnames <- list.files(path=file.path('..','Processes','FC_Matrix'), pattern="30_50") %>% as.list() # only the folder names (i.e. fID), (N=2244)

# # remove very young subjects (mostly controls) to avoid between-group Age difference
# df <- df %>% 
#   dplyr::filter(!(curr_ptsd_dx=='Control' & Age<11.4)) # (N=2798)

# fullnames of a type of data files (e.g. "AMC_sub-1132_FC_30_50.csv")
df <- df %>% mutate(sig_fullname = paste0(fID,"_FC_30_50.csv")) # (N=2931)

# merge SbjInfo.csv & brain data file list
df0_demcli <- df[df$sig_fullname %in% fnames,] # (N=2244) for demographic & clinical info!!!
```

## (2) Extract the seed-based sFC (tw=0, tp=100) & DFC (tw=30, tp=50, & other parameters)
```{r,echo=FALSE}
# parameters
# SFC (0,100) & DFC (different window width & overlaps in %)
fdtype <- c("FC_0_100", "FC_30_50", "FC_30_25", "FC_30_75", "FC_20_50", "FC_40_50")
# 4 seeds
fseed  <- c("Left-Amygdala","Right-Amygdala","Left-Hippocampus","Right-Hippocampus")
# roi info
froi   <- file.path('..','Data','Brain_Atlas_Schaefer400_FreeSurfer17.csv') %>% 
  fread() %>% .$Label_ggseg
# index of seeds in rois
idx <- fseed %>% sapply(function(x) which(froi %in% x)) # 407, 415, 406, 414 in order

# N_sbj
N_sbj <- df0_demcli %>% dim() %>% .[[1]]
# N_var (number of variables)
N_var <- length(fdtype) * length(fseed) * length(froi)

## Column names
# concatenate data type & seed, e.g. "FC_30_50_Left-Hippocampus"
Mnames <- outer(fdtype, fseed, function(x,y) paste(x,y,sep="_")) %>% t() %>% c()
# concatenate data type, seed, & target, e.g. "FC_0_100_Left-Hippocampus_to_lh_17Networks_LH_ContA_PFCl_3"
Mnames <- outer(Mnames, froi, function(x,y) paste(x,y,sep="_to_")) %>% t() %>% c()

# matrix of data file names (row=subject, column=individual file type)
# concatenate path & fID, e.g., "../Processes/FC_Matrix/AMC_sub-1132"
Mfn <- outer(file.path('..','Processes','FC_Matrix'), df0_demcli$fID,
             function(x,y) file.path(x,y)) %>% c() 
# concatenate data type & file extension, e.g., "FC_0_100.csv"
Mfn1 <- outer(fdtype, '.csv', function(x,y) paste(x,y,sep="")) %>% c()
# concatenate path, fID, data type, & file extension, e.g., "../Processes/FC_Matrix/AMC_sub-1132_FC_0_100.csv"
Mfn <- outer(Mfn, Mfn1, function(x,y) paste(x,y,sep="_")) 

# function to extract data from indexed columns in a given file
# Input
# -- fn, fullname of the data file
# -- idx, index of the specific columns
# Output
# -- a vector of the extracted values
myfun_extract <- function(fn, idx){
  return(
    fn %>% fread(select=as.vector(idx)) %>% as.matrix() %>% c()
  )
}

# function to concatenate values of the same row into a vector
# Input
# -- irow, the row index
# -- M, the matrix made by the previous function
# Output
# -- a vector of values of the same row
myfun_concatenate <- function(irow, M){
  return(M[,irow,] %>% c())
}

# extract data from indexed columns across datatype (cols) & subjects (rows)
system.time({
  print("Loading data!!! May be time consuming depending on the data size...")
  M <- Mfn %>% apply(c(1,2), myfun_extract, idx) 
  # No. data points per file x No. subjects x No. data type
  print("Completed! Data loaded!")
})

# concatenate the data of the same subject into a row in the matrix
system.time({
  print("Concatenating data per subject!!!")
  M <- seq(dim(M)[2]) %>% sapply(myfun_concatenate, M) %>% t() %>% as.data.frame()
  # No. subjects x No. data per subject (No. data points per file x No. data type)
  colnames(M) <- Mnames
  print("Completed!!! Data concatenation.")
})

# the merged demographic, clinical, & imaging data
system.time({
  df0 <- cbind(df0_demcli, M) # (2244x10452)
})

# save data
system.time({
  df0 %>% fwrite(file.path("..","Processes","Data_cleaned.csv"))
})


```

## (3) information of cleaned data
-- numeric, categorical
-- domain: demographic, clinical, DFC, SFC
-- brain atlas
```{r,echo=FALSE}
# list all variable names
df <- data.frame(VarName=colnames(df0), VarClass=NA)

# Set class: numeric or categorical, or BAD!!! (all NA or constants that could not be analyzed)
myfun_varclass <- function(col){
  if( all(is.na(col)) || length(unique(na.omit(col)))==1){
    return("NA or Constant")
  }else if (length(unique(col))>5) {
    # can't use is.numeric(col) in the expression, weird!!!
    return("Numeric")
  } else {
    return("Categorical")
  }
}
df$VarClass <- apply(df0, 2, myfun_varclass)
# set the class for SITE
df[df$VarName %in% c('SITE'), 'VarClass'] = 'Categorical' 

# Set order of categorical variables (if necessary)
df[df$VarName=="Sex", "OrderCategorical"] <- "Male;Female"
df[df$VarName=="curr_ptsd_dx", "OrderCategorical"] <- "Control;PTSD"


## Set domain 1: GROUP, demographic, clinical, DFC, SFC
df[df$VarName %in% c('curr_ptsd_dx'), 'VarDomain1'] = 'GROUP'
df[df$VarName %in% c('Age', 'Sex', 'curr_ptsd_sev_harmon', 'child_trauma_sev_harmon', 'life_adult_trauma_sev_harmon', 'depression_sev_harmon'), 'VarDomain1'] = 'Demographic and clinical'

name_brain_data <- df0 %>% select(starts_with(c('FC_0_100'))) %>% colnames()
df[df$VarName %in% name_brain_data, 'VarDomain1'] = 'SFC'

name_brain_data <- df0 %>% select(starts_with(c('FC_30_50'))) %>% colnames()
df[df$VarName %in% name_brain_data, 'VarDomain1'] = 'DFC'

# # Set domain 2: DFC_LAmyg, DFC_RAmyg, DFC_LHipp, DFC_RHipp, SFC_LAmyg, SFC_RAmyg, SFC_LHipp, SFC_RHipp
# name_brain_data <- df0 %>% select(starts_with("DFC_30_50_LAmyg_")) %>% colnames()
# df[df$VarName %in% name_brain_data, "VarDomain1"] = "DFC"

## Set atlas (brain atlas: Schaefer17_400 & FreeSurfer subcortical 17)
myfun_atlas <- function(str){
  if (startsWith(str, "FC_")){
    return(str_split(str, "_to_") %>% unlist() %>% .[2])
  } else {
    return(NA)
  }
}

df$atlas <- df$VarName %>% sapply(myfun_atlas)

# save data
fout <- file.path('..', 'Processes', 'Data_cleaned_info.csv')
df %>% fwrite(fout)
```


```{r,echo=FALSE}
# library(ggseg)
# plot(aseg)
# a <- aseg$data %>% select(c("label", "region"))
# 
# library(ggsegSchaefer)
# a <- tibble(label=brain_labels(schaefer17_400)) 
# a %>% fwrite('xxx.csv')
# b <- tibble(region=brain_regions(schaefer17_400))
# b %>% fwrite('xxx.csv')
# ggplot() +  geom_brain(atlas = schaefer17_400, 
#                        position = position_brain(hemi ~ side),
#                        show.legend = FALSE)
```

