---
title: "SDL_R_Clean"
author: "Delin Sun"
date: "2023-07-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aims

This R Markdown document aims at cleaning & organizing the data to meet the requirement of the DS package

## Packages
```{r, echo=FALSE}
if (!require("pacman")) {
  install.packages("pacman")
} # make sure that pacman is installed

pacman::p_load(tidyverse,    # data management
               plyr,         # data manegement
               data.table   # quick read & write files
)
```

## Load raw data files
Including:
--- subjects' demographic & clinical info
--- 4 seed-based dynamic rsFC (tw=30, tp=50) & static rsFC (tw=0, tp=100)
--- cleaned data's info: numeric/categorical, domain, brain atlas

## (1) subjects' demographic & clinical info
```{r, echo=FALSE}
# load SbjInfo_harmon.csv: harmonized clinical/behavioral info provided by Ahmed
df <-
  file.path('..', 'Data', 'delin_harmonized_updated_final.csv') %>% fread(na.strings=c('#NULL!', 'NA')) %>%
  distinct(fID, .keep_all = T) # all subjects' info (N=2931)

# clean & transform variables of interest
# Sex
df$Sex <- df$Sex %>% 
  as.factor() %>% 
  plyr::revalue(c("0"="Male",  "1"="Female")) # according to the defination per SITE

# Current PTSD diagnosis (curr_PTSD_dx)
df$curr_ptsd_dx <- df$CurrentPTSDDiagnosis %>% 
  as.factor() %>% 
  plyr::revalue(c("0"="Control","1"="PTSD"))

# remove subjects without clear curr_PTSD_dx, Age, Sex, or SITE info
# Age & Sex in fact do not have missing values
df <- df %>% 
  filter(!is.na(curr_ptsd_dx) & !is.na(Age) & !is.na(Sex) & !is.na(SITE)) # (N=2931)

# list all subjects' brain data files (one file per subject)
fnames <- list.files(path=file.path('..','Processes','FC_Matrix'), pattern="30_50") %>% as.list() # only the folder names (i.e. fID), (N=2244)

# # remove very young subjects (mostly controls) to avoid between-group Age difference
# df <- df %>% 
#   dplyr::filter(!(curr_ptsd_dx=='Control' & Age<11.4)) # (N=2798)

# fullnames of a type of data files (e.g. "AMC_sub-1132_FC_30_50.csv")
df <- df %>% mutate(sig_fullname = paste0(fID,"_FC_30_50.csv")) # (N=2931)

# merge SbjInfo.csv & brain data file list
df0_demcli <- df[df$sig_fullname %in% fnames,] # (N=2244) for demographic & clinical info!!!
```


## Extract the seed-based DFC (tw=30, tp=50) & sFC (tw=0, tp=100)
```{r,echo=FALSE}
# parameters
# SFC (0,100) & DFC (different window width & overlaps in %)
fdtype <- c("FC_0_100", "FC_30_50", "FC_30_25", "FC_30_75", "FC_20_50", "FC_40_50")
# 4 seeds
fseed  <- c("Left-Amygdala","Right-Amygdala","Left-Hippocampus","Right-Hippocampus")
# roi info
froi   <- file.path('..','Data','Brain_Atlas_Schaefer400_FreeSurfer17.csv') %>% 
  fread() %>% .$Label_ggseg
# N_sbj
N_sbj <- df0_demcli %>% dim() %>% .[[1]]
# N_var (number of variables)
N_var <- length(fdtype) * length(fseed) * length(froi)


# a big matrix to contain the data
M <- matrix(NA, nrow=N_sbj, ncol=N_var)
# names of the columns
# concatenate data type & seed first, e.g. "FC_30_50_Left-Hippocampus"
Mnames <- outer(fdtype, fseed, function(x,y) paste(x,y,sep="_")) %>% t() %>% c()
# concatenate data type, seed, & target, e.g. "FC_0_100_Left-Hippocampus_to_lh_17Networks_LH_ContA_PFCl_3"
Mnames <- outer(Mnames, froi, function(x,y) paste(x,y,sep="_to_")) %>% t() %>% c()





# list files of this subject
fn <- file.path('..','Processes','FC_Matrix') %>% list.files(pattern=df0_demcli$fID[[1]])

# get one data file for an example
M <- file.path('..','Processes',"FC_Matrix",df0_demcli$sig_fullname[[1]]) %>% 
  fread()
colnames(M) <- df_roi$Label_ggseg
rownames(M) <- df_roi$Label_ggseg

# only the values related to the seeds of interest
a <- M %>% select(fseed)
# 
col_row_names <- outer(colnames(a), rownames(a), function(x,y) paste(x,y,sep="_")) %>% t() %>% c()

b <- a %>% as.matrix() %>% c()

```

## (2) 4 seed-based dynamic rsFC (tw=30, tp=50) & sFC (tw=0, tp=100)
```{r,echo=FALSE}
# DFC filenames & prefix for re-organizations
df_FC_info <-
  tibble(
    fpre = c(
      'DFC_30_50_LAmyg',
      'DFC_30_50_RAmyg',
      'DFC_30_50_LHipp',
      'DFC_30_50_RHipp',
      'SFC_LAmyg',
      'SFC_RAmyg',
      'SFC_LHipp',
      'SFC_RHipp'
    ),
    fname = c(
      'sd_30_50_seed=FreeSurfer_Left.Amygdala',
      'sd_30_50_seed=FreeSurfer_Right.Amygdala',
      'sd_30_50_seed=FreeSurfer_Left.Hippocampus',
      'sd_30_50_seed=FreeSurfer_Right.Hippocampus',
      'sd_0_100_seed=FreeSurfer_Left.Amygdala',
      'sd_0_100_seed=FreeSurfer_Right.Amygdala',
      'sd_0_100_seed=FreeSurfer_Left.Hippocampus',
      'sd_0_100_seed=FreeSurfer_Right.Hippocampus'
    )
  )

# function to load brain data & change column names & merge
# Input
# --- df_FC_info, dataframe of data filenames and prefix
# --- df0_demcli, dataframe of demographic & clinical info
# --- fdir, the path to the directory of data file
# Output
# --- a dataframe with merged data (row:subject, col:seed-to-region DFC/SFC)
SDL_Merge <-function(df_FC_info, df0_demcli, fdir){
  # use the column of fID to start merging data (also limit the range of subjects)
  df1 <- df0_demcli['fID']
  for (i in seq(dim(df_FC_info)[[1]])){
    # fullname of the data file
    fin  <- fdir %>% file.path(paste0(df_FC_info$fname[[i]], '.csv'))
    # read data file
    df <- fread(fin) # (2588 x 418)
    # add prefix to columns except the last column (i.e. fID)
    colnames(df)[-ncol(df)] <- paste0(df_FC_info$fpre[[i]], '_', colnames(df)[-ncol(df)])
    df1 <- df1 %>% merge(df, by='fID')
  }
  
  # fID as the rownames & remove the column of fID
  df <- df1
  rownames(df) <- df[,1] # fID as rownames
  df[,1] <- NULL # remove the column of fID
  
  # remove rows with only NA or 0
  df <- df[rowSums(df != 0, na.rm=TRUE) > 0,] # (2537 x 3336)
  
  # add fID as a column
  df$fID <- rownames(df)
  
 # merge demographic/clinical info and brain data
  df0_demcli %>% merge(df, by='fID') %>% 
    return()
}

# directory
fdir <- file.path('..', 'Results', 'ROI-to-ROI')

# run function
df0 <- SDL_Merge(df_FC_info, df0_demcli, fdir) # (2537 x 3370)

# save data
fout <- file.path('..', 'Data', 'Data_cleaned.csv')
df0 %>% fwrite(fout)

```

## (3) information of cleaned data
-- numeric, categorical
-- domain: demographic, clinical, DFC, SFC
-- brain atlas
```{r,echo=FALSE}
# list all variable names
df <- tibble(VarName = colnames(df0),
             VarClass = NA)

## Set class: numeric or categorical, or BAD!!! (all NA or constants that could not be analyzed)
df$VarClass <- apply(df0, 2, function(x)
  ifelse(length(unique(x)) > 5,
         'numeric',
         'Categorical')) # categorical variables if No. of unique values > 5

df[df$VarName %in% c('SITE'), 'VarClass'] = 'Categorical' # adjust some variables

## Set domain 1: GROUP, demographic, clinical, DFC, SFC
df[df$VarName %in% c('curr_ptsd_dx'), 'VarDomain1'] = 'GROUP'
df[df$VarName %in% c('Age', 'Sex', 'curr_ptsd_sev_harmon', 'child_trauma_sev_harmon', 'life_adult_trauma_sev_harmon', 'depression_sev_harmon'), 'VarDomain1'] = 'Demographic and clinical'

name_brain_data <- df0 %>% select(starts_with(c('DFC_'))) %>% colnames()
df[df$VarName %in% name_brain_data, 'VarDomain1'] = 'DFC'

name_brain_data <- df0 %>% select(starts_with(c('SFC_'))) %>% colnames()
df[df$VarName %in% name_brain_data, 'VarDomain1'] = 'SFC'

# # Set domain 2: DFC_LAmyg, DFC_RAmyg, DFC_LHipp, DFC_RHipp, SFC_LAmyg, SFC_RAmyg, SFC_LHipp, SFC_RHipp
# name_brain_data <- df0 %>% select(starts_with("DFC_30_50_LAmyg_")) %>% colnames()
# df[df$VarName %in% name_brain_data, "VarDomain1"] = "DFC"

## Set atlas (brain atlas: Schaefer17_400 & FreeSurfer subcortical 17)
fatlas <- 'Brain_Atlas_Schaefer400_FreeSurfer17.csv'
df_atlas <- file.path('..', 'Data', fatlas) %>% fread() # load brain atlas

# function to remove multiple prefix from column names
# Input
# --- df0, dataframe of all cleaned data
# --- df_FC_info, dataframe of prefix to be removed
SDL_noprefix <- function(df0, df_FC_info){
  names_df <- df0 %>% colnames()
  for (i in seq(dim(df_FC_info)[[1]])){
    names_df <- names_df %>% str_replace(paste0(df_FC_info$fpre[[i]],'_'), '')
  }
  return(names_df)
}
# extract data file colnames (after removing prefix) to match the atlas
names_df <- df0 %>% SDL_noprefix(df_FC_info)

# index of colnames that match the atlas
idx <- match(names_df, df_atlas$ROI_Data)
df$Atlas_Source <- NA
df$Atlas_Source[!is.na(idx)] <- fatlas # atlas source file name
df$Atlas_Label  <- df_atlas$Label_ggseg[idx] # atlas label
df$Atlas_Region <- df_atlas$region_ggseg[idx]# atlas region (or 17 network name)
# coordinates
df$Atlas_R      <- df_atlas$R[idx]
df$Atlas_A      <- df_atlas$A[idx]
df$Atlas_S      <- df_atlas$S[idx]


# save data
fout <- file.path('..', 'Data', 'Data_cleaned_info.csv')
df %>% fwrite(fout)
```


```{r,echo=FALSE}
# library(ggseg)
# plot(aseg)
# a <- aseg$data %>% select(c("label", "region"))
# 
# library(ggsegSchaefer)
# a <- tibble(label=brain_labels(schaefer17_400)) 
# a %>% fwrite('xxx.csv')
# b <- tibble(region=brain_regions(schaefer17_400))
# b %>% fwrite('xxx.csv')
# ggplot() +  geom_brain(atlas = schaefer17_400, 
#                        position = position_brain(hemi ~ side),
#                        show.legend = FALSE)
```

